---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Grisma Sinya"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 4
    fig_width: 4
    highlight: zenburn
    theme: journal
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns. 
The variables included in the dataframe are: dataset,x and y.

### Exercise 2

#Plot y vs. x for the dino dataset:
```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#Correlation coefficient between x and y for the dataset:
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient is -0.0645.

### Exercise 3

#Plot y vs. x for the star dataset:
```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#Correlation coefficient between x and y for the dataset:
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for star dataset is -0.0629611.

### Exercise 4

#Plot y vs. x for the circle dataset:
```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
#Correlation coefficient between x and y for the dataset:
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient is -0.06834336. There is not much difference between this value and the r of dino(-0.0645). 

### Exercise 5
```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
  ```
  
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

